End-user Web Scraping For Customization

### 2021-02-13 paper.tex
initial latex compile

% -*- coding: utf-8; -*-
% vim: set fileencoding=utf-8 :
\documentclass[english]{programming}
%% First parameter: the language is 'english'.
%% Second parameter: use 'submission' for initial submission, remove it for camera-ready (see 5.1)

\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}

@@

\usepackage[backend=biber]{biblatex}
\addbibresource{references2.bib}

@@

%%% The following is specific to <Programming'20> Companion-CCS and the paper
%%% 'Wildcard: Spreadsheet-Driven Customization of Web Applications'
%%% by Geoffrey Litt and Daniel Jackson.
%%%
%%% (Author note: Commented out this info, doesn't seem to fit with this template)
% \setcopyright{acmlicensed}
% \acmPrice{}
% \acmDOI{10.1145/3397537.3397541}
% \acmYear{2020}
% \copyrightyear{2020}
% \acmSubmissionID{prog20ccs-id3-p}
% \acmISBN{978-1-4503-7507-8/20/03}
% \acmConference[<Programming'20> Companion]{Companion Proceedings of the 4th International Conference on the Art, Science, and Engineering of Programming}{March 23--26, 2020}{Porto, Portugal}
% \acmBooktitle{Companion Proceedings of the 4th International Conference on the Art, Science, and Engineering of Programming (<Programming'20> Companion), March 23--26, 2020, Porto, Portugal}

\begin{document}

\title{Wildcard: Spreadsheet-Driven Customization of Web Applications}
\subtitle{}% optional

\author{Geoffrey Litt}
\authorinfo{is a PhD student at MIT in the Software Design Group. His research focuses on programming languages and environments, particularly tools for end user programming and live programming. Contact him at \email{glitt@mit.edu}.}
\author{Daniel Jackson}
\authorinfo{is Professor in the Department of Electrical Engineering and Computer Science at MIT,  a MacVicar teaching fellow, and Associate Director of the Computer Science and Artificial Intelligence Laboratory. He leads the Software Design Group. Contact him at \email{dnj@csail.mit.edu}.}
\affiliation{Massachusetts Institute of Technology}

\keywords{end-user programming, software customization, web browser extensions} % please provide 1--5 keywords

%%%%%%%%%%%%%%%%%%
%% These data MUST be filled for your submission. (see 5.3)
\paperdetails{
  %% perspective options are: art, sciencetheoretical, scienceempirical, engineering.
  %% Choose exactly the one that best describes this work. (see 2.1)
  perspective=art,
  %% State one or more areas, separated by a comma. (see 2.2)
  %% Please see list of areas in http://programming-journal.org/cfp/
  %% The list is open-ended, so use other areas if yours is/are not listed.
  area={Programming environments, Visual and live programming},
  %% You may choose the license for your paper (see 3.)
  %% License options include: cc-by (default), cc-by-nc
  % license=cc-by-sa,
}
%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%
%% These data are provided by the editors. May be left out on submission.
%\paperdetails{
%  submitted=2016-08-10,
%  published=2016-10-11,
%  year=2016,
%  volume=1,
%  issue=1,
%  articlenumber=1,
%}
%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Please go to https://dl.acm.org/ccs/ccs.cfm and generate your Classification
% System [view CCS TeX Code] stanz and copy _all of it_ to this place.
%% From HERE
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011066.10011069</concept_id>
<concept_desc>Software and its engineering~Integrated and visual development environments</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Integrated and visual development environments}
% To HERE
%%%%%%%%%%%%%%%%%%%%%%%

\maketitle

% Please always include the abstract.
% The abstract MUST be written according to the directives stated in
% http://programming-journal.org/submission/
% Failure to adhere to the abstract directives may result in the paper
% being returned to the authors.
\begin{abstract}
Many Web applications do not meet the precise needs of their users.
Browser extensions offer a way to customize web applications, but most
people do not have the programming skills to implement their own
extensions.

In this paper, we present \emph{spreadsheet-driven customization}, a
technique that enables end users to customize software without doing any
traditional programming. The idea is to augment an application's UI with
a spreadsheet that is synchronized with the application's data. When the
user manipulates the spreadsheet, the underlying data is modified and
the changes are propagated to the UI, and vice versa.

We have implemented this technique in a prototype browser extension
called Wildcard. Through concrete examples, we demonstrate that Wildcard
can support useful customizations---ranging from sorting lists of search
results to showing related data from web APIs---on top of existing
websites. We also present the design principles underlying our
prototype.

Customization can lead to dramatically better experiences with software.
We think that spreadsheet-driven customization offers a promising new
approach to unlocking this benefit for all users, not just programmers.

This paper is best viewed in the online version (\url{https://www.geoffreylitt.com/wildcard/salon2020}), which includes videos demonstrating the interface.
\end{abstract}

@@

Web applications often don't meet the precise needs of their users.
Sometimes there is a browser extension available to patch an issue, and
if the user is a programmer they might be able to fix it themselves. But
for most people, the only recourse is to complain to the developers, or,
more likely, to simply give up. Back in 1977, in \emph{Personal Dynamic
Media} \autocite{kay1977}, Alan Kay envisioned personal computing as a
medium that let a user ``mold and channel its power to his own needs,''
but today, software behaves more like concrete than clay.

In this paper, we present \emph{spreadsheet-driven customization}, a
technique that enables end users to customize software without doing any
traditional programming. The idea is to augment an application's UI with
a spreadsheet that is synchronized with the application's data. When the
user manipulates the spreadsheet, the underlying data is modified and
the changes are propagated to the UI, and vice versa.

We have implemented this technique in a prototype browser extension
called Wildcard and used it to build demos which suggest that this
paradigm can support useful customizations, ranging from sorting lists
of data to adding whole new features to applications (shown in
Section~\ref{sec:demos}).

\begin{figure}
\hypertarget{fig:overview}{%
\centering
\includegraphics{media/overview-300dpi.png}
\caption{An overview of spreadsheet-driven
customization}\label{fig:overview}
}
\end{figure}

Our approach requires extracting structured data from the user
interfaces of existing applications, but we hide the complexity of data
extraction from end users. Programmers write \emph{site adapters} which
use web scraping techniques to extract structured data from existing
applications and map it to the spreadsheet table. Our prototype suggests
that it is possible to implement site adapters for real websites;
Section~\ref{sec:implementation} describes some of the techniques and
challenges involved.

Spreadsheet-driven customization is based on three design principles,
described in Section~\ref{sec:design-principles}:

\begin{itemize}
\tightlist
\item
  \textbf{Expose a universal structure}: By mapping the data in all
  applications to the same universal table abstraction, Wildcard enables
  users to learn a generic customization toolkit that they can apply to
  any site.
\item
  \textbf{Low floor, high ceiling}: Wildcard provides an easy entry
  point for end users, since small tweaks like sorting data can be
  performed with a single click. At the same time, it also supports a
  variety of richer customizations, like adding private annotations to a
  webpage or joining in related data from a web API.
\item
  \textbf{Design for an ecosystem of users}: Spreadsheet-driven
  customization combines the efforts of programmers and end users,
  rather than putting the full burden on end users. We also envision a
  role for first party developers to help make their applications more
  customizable.
\end{itemize}

Prior work \autocite{mccutchen2016,benson2014,chang2014} has enabled end
users to create ``spreadsheet-driven applications'' which use
spreadsheets as a backing data layer. Spreadsheet-driven
\emph{customization} applies this idea in a different context:
customizing existing software, rather than building new software from
scratch. Our technique does not require that the application actually be
backed by a spreadsheet; it merely uses the spreadsheet as an interface
for viewing and modifying the internal state of the application. In
Section~\ref{sec:related-work}, we describe further how Wildcard relates
to existing work on spreadsheet-driven apps, as well as work in other
areas like web customization and web scraping.

The Wildcard extension is currently an early research prototype. We plan
to continue testing the system with our own use cases to explore how the
spreadsheet abstraction maps to real websites and customization needs.
Eventually we plan to release the tool publicly in order to learn from
real use cases, discover usability challenges, and to test the
feasibility of building and maintaining site adapters.
Section~\ref{sec:conclusion} describes open questions we plan to
continue exploring, as well as our future plans.

\hypertarget{sec:demos}{%
\section{Demos}\label{sec:demos}}

Here are some examples of using Wildcard to customize websites in useful
ways.{ These demos are best viewed as videos in the online version of
this paper (\url{https://www.geoffreylitt.com/wildcard/salon2020}).}

\begin{figure}
\hypertarget{fig:airbnb-demo}{%
\centering
\includegraphics{media/airbnb-demo-300dpi.png}
\caption{Using Wildcard to augment the Airbnb search page for booking
accommodations}\label{fig:airbnb-demo}
}
\end{figure}

\hypertarget{augmenting-search-results}{%
\subsection{Augmenting search results}\label{augmenting-search-results}}

In 2012, the travel site Airbnb removed the ability to sort
accommodation searches by price. Users could still filter by price
range, but could no longer view the cheapest listings first. Many users
complained that the change seemed hostile to users. ``It's so
frustrating! What is the logic behind not having this function?'' said
one user on the
\href{https://community.withairbnb.com/t5/Hosting/Sorting-listing-by-price/td-p/559404}{Airbnb
support forum}. Alas, the feature remains missing to this day.

Using Wildcard, the user can fix this omission, while leaving the page's
design and the rest of its functionality unchanged.{
Figure~\ref{fig:airbnb-demo} shows an overview of augmenting the Airbnb
site.} First, the user opens up the Wildcard panel, which shows a table
corresponding to the search results in the page. As they click around in
the table, the corresponding row in the page is highlighted to indicate
the mapping between the views.

Then, the user clicks on the price column header to sort the spreadsheet
and the Airbnb UI by price{ (Figure~\ref{fig:airbnb-demo}, Note A)}.
They also filter to listings with a user rating above 4.5 (another
feature missing in the original Airbnb UI).

After manipulating the data, the user closes the table view and
continues using the website. Because the application's UI usually has a
nicer visual design than a spreadsheet, Wildcard does not aim to replace
it---at any time, the user can use either the UI, the spreadsheet, or
both together.

Many websites that show lists of data also offer actions on rows in the
table, like adding an item to a shopping cart. Wildcard has the ability
to make these ``row actions'' available in the data table through the
site adapter. In the Airbnb UI, saving multiple listings to a Favorites
list requires tediously clicking through them one by one. Using Wildcard
row actions, the user can select multiple rows and favorite all of them
with a single click{ (Figure~\ref{fig:airbnb-demo}, Note B)}. Similarly,
the user can open the detailed pages for many listings at once.

Next, the user wants to jot down some notes about each listing. To do
this, they type some notes into an additional column in each row, and
the notes appear inside the listings in the original UI{
(Figure~\ref{fig:airbnb-demo}, Note C)}. The annotations are saved in
the browser and associated with the backend ID of the listing, so they
will appear in future browser sessions that display the same listing.

Wildcard also includes a formula language that enables more
sophisticated customizations. When traveling without a car, it's useful
to evaluate potential places to stay based on how walkable the
surroundings are. Using a formula, the user can integrate Airbnb with
Walkscore, an API that rates the walkability of any location on a 1-100
scale. When the user calls the \texttt{walkscore} formula with the
listing's latitude and longitude as arguments, it returns the walk score
for that location and shows it as the cell value. Because the cell's
contents are injected into the page, the score also appears in the UI{
(Figure~\ref{fig:airbnb-demo}, Note D)}.

\hypertarget{snoozing-todos}{%
\subsection{Snoozing todos}\label{snoozing-todos}}

\begin{figure}
\hypertarget{fig:todomvc-demo}{%
\centering
\includegraphics{media/todomvc-demo-300dpi.png}
\caption{Using Wildcard to add a ``snooze'' feature to the TodoMVC todo
list app}\label{fig:todomvc-demo}
}
\end{figure}

In addition to fetching data from other sources, Wildcard formulas can
also perform computations. In this example, the user would like to
augment the TodoMVC todo list app with a ``snooze'' feature, which will
temporarily hide a todo from the list until a certain date.{
Figure~\ref{fig:todomvc-demo} shows an overview of this customization.}

The user opens the table view, which shows the text and completed status
of each todo. They start the customization by adding a new column to
store the snooze date for each todo{ (Figure~\ref{fig:todomvc-demo},
Note A)}.

The next step is to hide snoozed todos. The user creates a
\texttt{snoozed?} column, which uses a formula to compute whether a todo
is snoozed---i.e., whether it has a snooze date in the future{
(Figure~\ref{fig:todomvc-demo}, Note B)}. Then, they simply filter the
table to hide the snoozed todos{ (Figure~\ref{fig:todomvc-demo}, Note
C)}.

Because the built-in \texttt{NOW()} function always returns the current
datetime, snoozed todos will automatically appear once their snooze date
arrives.

Because this implementation of snoozing was built on the spreadsheet
abstraction, it is completely decoupled from this particular todo list
app. We envision that users could share these types of customizations as
generic browser extensions, which could be applied to any site supported
by Wildcard with no additional effort.

\hypertarget{adding-a-custom-datepicker}{%
\subsection{Adding a custom
datepicker}\label{adding-a-custom-datepicker}}

\begin{figure}
\hypertarget{fig:expedia-demo}{%
\centering
\includegraphics{media/expedia-demo-300dpi.png}
\caption{Using Wildcard to augment the Expedia page for booking a
flight}\label{fig:expedia-demo}
}
\end{figure}

It might seem that Wildcard is only useful on websites that display
lists of tabular data, but the table metaphor is flexible enough to
represent many types of data. For example, a flight search form on
Expedia can be represented as a single row, with a column corresponding
to each input{ (Figure~\ref{fig:expedia-demo}, Note A)}.

In some of the previous examples, the table cells were read-only
(because users can't, for example, change the name or price of an Airbnb
listing). In this case, the cells are writable, which means that changes
in the table are reflected in the form inputs. This becomes especially
useful when combined with GUI widgets that can edit the value of a table
cell.

Filling in dates for a flight search often requires a cumbersome
workflow: open up a separate calendar app, find the dates for the trip,
and then carefully copy them into the form. In Wildcard, the user can
avoid this by using a datepicker widget that shows the user's personal
calendar events{ (Figure~\ref{fig:expedia-demo}, Note B)}. The user can
directly click on the correct date, and it gets inserted into both the
spreadsheet and the original form.

In this section we've presented just a few use cases for
spreadsheet-driven customization, to suggest some possibilities of the
paradigm. We think the spreadsheet model is flexible enough to support a
wide range of other useful modifications while remaining familiar and
easy to use.

@@

Wildcard is written in Typescript. It is currently injected into pages
using the \href{https://www.tampermonkey.net/}{Tampermonkey} userscript
manager, but in the future we plan to deploy it as a standalone browser
extension to make it easier to install.

In order to promote extensibility, Wildcard is implemented as a small
core program along with several types of plugins: site adapters,
formulas, and cell editors. The core contains functionality for
displaying the data table and handling user interactions, and is built
on the \href{https://handsontable.com/}{Handsontable} Javascript
library.

\begin{figure}
\hypertarget{fig:architecture}{%
\centering
\includegraphics{media/architecture-300dpi.png}
\caption{The architecture of the Wildcard
prototype}\label{fig:architecture}
}
\end{figure}

Site adapters are a key part of Wildcard, since they specify the
bidirectional connection between the web page and its structured data
representation. Wildcard represents data in a relational table with
named and typed columns, and provides an interface for concisely
expressing how the DOM should be mapped to this structure. For example,
here is a code snippet for extracting the name of an Airbnb listing.

\begin{Shaded}
\begin{Highlighting}[]
\OperatorTok{\{}
  \CommentTok{// Field metadata:}
\NormalTok{  fieldName}\OperatorTok{:} \StringTok{"name"}\OperatorTok{,}
\NormalTok{  type}\OperatorTok{:} \StringTok{"text"}\OperatorTok{,}
\NormalTok{  readOnly}\OperatorTok{:} \KeywordTok{true}\OperatorTok{,}

  \CommentTok{// Function to extract DOM element:}
\NormalTok{  el}\OperatorTok{:}\NormalTok{ (row) }\KeywordTok{=>} \VariableTok{row}\OperatorTok{.}\FunctionTok{querySelector}\NormalTok{(}\StringTok{".\_1ebt2xej"}\NormalTok{)}\OperatorTok{,}
\OperatorTok{\}}
\end{Highlighting}
\end{Shaded}

Sometimes, more advanced scraping techniques are necessary to extract
data from the application. For example, we have prototyped a mechanism
for site adapters to observe AJAX requests made by the browser and
extract data directly from JSON responses. This mechanism was used to
implement the Airbnb Walkscore example, since latitude and longitude
aren't shown in the Airbnb UI, but they are available in AJAX responses.
This technique seems promising because AJAX responses already contain
data in a structured form, and web applications are increasingly loading
data using AJAX. Another technique we might consider is enabling site
adapters to scrape data across multiple pages for paginated lists of
results (as explored in \autocite{huynh2006}).

Because Wildcard requires a live bidirectional connection between the UI
and the structured data, there are some additional challenges beyond
those typically associated with web scraping.

First, the site adapter needs to support sending updates from the table
to the original page. We have made this fairly straightforward, because
most DOM manipulation is not performed directly by the site adapter.
Instead, Wildcard automatically mutates the DOM to reflect the
spreadsheet state, using the same specification that was used to extract
the data. The only exception to this is row actions (like favoriting an
Airbnb listing), which are implemented as Javascript functions that can
perform arbitrary behaviors like simulating clicks on buttons or
mutating the DOM.

Another challenge is triggering updates to the spreadsheet data in
response to UI changes that happen after initial page load. Site
adapters are responsible for recognizing these changes by observing the
DOM. So far, we have been able to use event listeners and the
MutationObserver API to successfully observe changes, but it may prove
challenging to observe changes on some sites only through the DOM.

>>>>

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%%
%% IMPORTANT NOTICE:
%%
%% For the copyright see the source file.
%%
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%%
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%%
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf,10pt]{acmart}

@@

@@

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{End-user Web Scraping For Customization}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.

\author{Kapaya Katongo}
\affiliation{%
  \institution{MIT CSAIL}
  \city{Cambridge, MA}
  \country{USA}
}
\email{kkatongo@mit.edu}

\author{Geoffrey Litt}
\affiliation{%
  \institution{MIT CSAIL}
  \city{Cambridge, MA}
  \country{USA}
}
\email{glitt@mit.edu}

\author{Daniel Jackson}
\affiliation{%
  \institution{MIT CSAIL}
  \city{Cambridge, MA}
  \country{USA}
}
\email{dnj@csail.mit.edu}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
% \renewcommand{\shortauthors}{Trovato and Tobin, et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Websites are malleable: users can install browser extensions and run
  arbitrary Javascript in the developer console to change them. However,
  this malleability is only accessible to programmers with knowledge of
  HTML, CSS, Javascript and the DOM. To broaden access to customization,
  our prior work developed an approach that empowers end-users to
  customize websites without traditional programming via a browser
  extension called Wildcard. Wildcard's customizations are powered by
  web scraping adapters which are currently written in Javascript by
  programmers. This means that end-users can only customize a website if
  a programmer has written an adapter for it. Furthermore, end-users do
  not have the ability to extend adapters in order to perform new
  customizations or repair adapters to fix broken customizations.

  In this paper, we extend Wildcard with a new system for \emph{end-user
  web scraping for customization} which enables end-users to create,
  extend and repair adapters by demonstration. We describe three design
  principles that guided our system's development and are applicable to
  other end-user web scraping and customization systems: (a) users
  should be able to scrape data and use it in a single, unified
  environment, (b) users should be able to extend and repair the
  programs that scrape data via demonstration and (c) users should
  receive live feedback during their demonstrations.

  We have successfully used our system to create, extend and repair
  adapters by demonstration on a variety of websites. We provide example
  usage scenarios that showcase each of our design principles.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
%% From HERE
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011066.10011069</concept_id>
<concept_desc>Software and its engineering~Integrated and visual development environments</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Integrated and visual development environments}
% To HERE

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{end-user programming, software customization, web browser extensions}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
%\begin{teaserfigure}
%  \includegraphics[width=\textwidth]{sampleteaser}
%  \caption{Seattle Mariners at Spring Training, 2010.}
%  \Description{Enjoying the baseball game from the third-base
%  seats. Ichiro Suzuki preparing to bat.}
%  \label{fig:teaser}
%\end{teaserfigure}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

@@

Many websites on the internet do not meet the exact needs of all of
their users. End-user web customization systems like Chickenfoot
\citep{bolin2005}, Thresher \citep{hogue2005}, Sifter \citep{huynh2006}
and Vegemite {[}lin2009{]} help users tweak and adapt websites to fit
their unique requirements, ranging from reorganizing or annotating
content on the website to automating common tasks. In our prior work, we
presented Wildcard \citep{litt2020a}, a customization system which
enables end-users to customize websites through direct manipulation. It
does this by augmenting websites with a table view that shows their
underlying structured data. The table is bidirectionally synchronized
with the original website, so end-users can easily customize the website
by interacting with the table, including sorting and filtering data,
adding annotations, and running computations in a spreadsheet formula
language.

Wildcard has a key limitation. In order to enable end-users to customize
a website, a Javascript programmer first needs to code an adapter that
specifies how to scrape the website content and set up a bidirectional
synchronization with Wildcard's table view. Take Alice, an end-user who
uses Wildcard to customize her experience on Google Scholar as shown
above. Wildcard's sorting customization gives her the power to sort
publications by title which the website does not natively allow. She
thinks this will be useful on Weather.com to sort the ten day forecast
by the weather descriptions so that she can quickly find all the sunny
days. Unfortunately, a programmer has not coded an adapter for
Weather.com so Alice is unable to customize it. Additionally, if the
adapter for Google Scholar stops functioning when the website changes,
Alice has no recourse to repair it on her own.

In this paper, we describe an addition to Wildcard: a system that
enables end-users to create, extend and repair website adapters by
demonstration within the browser. Using this scraping system, an
end-user can perform end-to-end web customizations using Wildcard on
arbitrary websites, without ever needing to code an adapter. Through a
series of examples, we show that end-users can utilize our system to
successfully create Wildcard adapters on a variety of websites via
demonstration (Section~\ref{sec:demos}). We also describe key aspects of
our system and how web scraping for customization reveals a constraint
that simplifies the \emph{wrapper induction} \citep{kushmerick2000} task
used to generalize user demonstrations
(Section~\ref{sec:implementation}).

Our key contribution is a set of three design principles that guided the
development of our system, which also offer insights that might be
applied to other end-user web scraping and customization tools
(Section~\ref{sec:design-principles}):

\begin{itemize}
\tightlist
\item
  \textbf{Unified Environment}: Users should be able to scrape data and
  interact with the scraped data in a single, unified environment. This
  minimizes the barrier to fluidly switching back and forth between the
  two tasks, rather than treating them as entirely independent tasks.
\item
  \textbf{Editing By Demonstration}: Users should be able to not only
  create programs for scraping data by demonstration, but also extend
  and repair the programs by demonstration. This enables users to build
  on other user's work, and is especially important in the context of
  web scraping since programs that scrape data sometimes break as the
  underlying website changes.
\item
  \textbf{Live Programming}: Users should receive live feedback as they
  perform demonstrations. The system should indicate how it is
  generalizing from the user's example and what the resulting data will
  look like, so that the user can adjust their demonstrations on the fly
  and quickly arrive at the desired result.
\end{itemize}

Finally, we share our broader vision for web scraping for customization,
and some opportunities for future work, including a proposal for how
Wildcard's spreadsheet-like formula language might augment
demonstrations to provide end-users with more expressiveness in the web
scraping process (Section~\ref{sec:conclusion}).

\hypertarget{sec:demos}{%
\section{Motivating Examples}\label{sec:demos}}

In this section, we show how end-users can create, extend and repair
adapters for Wildcard via demonstration.

\hypertarget{creating-an-adapter}{%
\subsection{Creating An Adapter}\label{creating-an-adapter}}

Alice, our end-user from Section~\ref{sec:introduction}, wants to
customize her experience on Weather.com by sorting the ten-day forecast
based on the description of the weather on each day, allowing her to
easily view all the sunny days. She starts the adapter creation process
by clicking a context menu item within the Weather.com page, and hovers
over a data value she might like to scrape.

The system provides live feedback as Alice hovers, demonstrating the
\textbf{live programming} principle:

\begin{itemize}
\tightlist
\item
  The selected row of data is annotated in the page with a border, to
  indicate that she will be demonstrating values from within that row.
\item
  The selected column of data is highlighted in the page with a green
  background, to show how the system has generalized her demonstration
  across all the rows in the data.
\item
  A table view appears at the bottom of the screen, and displays how the
  values will appear in the data table.
\end{itemize}

Alice tries hovering over several other elements in the page, taking
advantage of the live feedback environment to decide what data would be
useful. After considering several options, she decides to save the date
field in the first column of the table, and commits the action by
clicking.

Next, she performs a similar process to fill the next column with the
weather descriptions. After filling both columns, she also tries
hovering over previously scraped data, and the toolbar at the top of the
page indicates which column corresponds to the previously scraped data.
Finally, she ends the adapter creation process and is able to
immediately sort the forecast by the weather description column, because
Wildcard provides a \textbf{unified environment} that combines both
scraping and customizing:

\hypertarget{extending-an-adapter}{%
\subsection{Extending An Adapter}\label{extending-an-adapter}}

Alice has previously used Wildcard to customize timeanddate.com. In
addition to sorting the list of holidays in a year by the day of the
week, she also wants to sort them by category so she can view all the
federal holidays together. Previously, she would have needed to find a
programmer to help her edit the adapter code to incorporate this
additional data, but using our system's support for \textbf{editing by
demonstration}, Alice can extend the adapter herself.

While viewing the website, she clicks the ``Edit Adapter'' button above
the Wildcard table to initiate the adapter editing process. As she
hovers over the currently scraped values, the columns they belong to are
highlighted. Finally, she clicks on ``Federal Holiday'' to add the new
column of data and saves the changes. Alice then proceeds to sort the
list by the type of holiday without the intervention of a programmer.

\hypertarget{repairing-an-adapter}{%
\subsection{Repairing An Adapter}\label{repairing-an-adapter}}

Alice next visits Google Scholar to look up references for her thesis
project. Unfortunately, the customization she had applied to sort
publications by their title (which is not natively supported by Google
Scholar) is no longer working. In fact, the column in the Wildcard table
that contained all the publication titles is empty, because the
website's internals changed and broke the adapter's scraping logic.
Alice can repair this on her own, again taking advantage of
\textbf{editing by demonstration}.

Alice initiates the editing process, and initially hovers over the
desired value to demonstrate the column she wants to scrape. However,
the \textbf{live programming} interface indicates to her that the values
would be populated into column D; instead, she wants the values to be
inserted into column A where they previously appeared. So, Alice clicks
on the symbol for column A to indicate that she wants to scrape the
values into that column. She then proceeds to re-apply her customization
to the website by sorting the publications by their title without the
intervention of a programmer.

@@

We implemented our end-user web scraping system as an addition to the
Wildcard browser extension. We start by describing our implementations
of row and column generalization, live programming, and editing by
demonstration, and then discuss some of the current limitations of our
system.

\hypertarget{generalization-algorithms}{%
\subsection{Generalization Algorithms}\label{generalization-algorithms}}

In order to generate reusable scrapers from user demonstrations, our
system solves the \emph{wrapper induction} \citep{kushmerick2000} task:
generalizing from a small set of user-provided examples to a scraping
specification that will work on other parts of the website, and on
future versions of the website.

We take an approach similar to that used in other tools like Vegemite
\citep{lin2009} and Sifter \citep{huynh2006}:

\begin{itemize}
\tightlist
\item
  We generate a single \emph{row selector} for the website: a CSS
  selector that returns a set of DOM elements corresponding to
  individual rows of the table.
\item
  For each column in the table, we generate a \emph{column selector}, a
  CSS selector that returns the element containing the column value
  within that row.
\end{itemize}

One important difference is that our algorithm only accepts row elements
that have direct siblings with a similar structure. We refer to this as
the \emph{row-sibling} constraint. Later in this section, we describe
how the constraint provides a useful simplification of the wrapper
induction task and discuss the resulting limitations this puts on our
system in a section that follows.

When a user first demonstrates a column value, the generalization
algorithm is responsible for turning the demonstration into a row
selector that will correctly identify all the row elements in the
website and a column selector that will correctly identify the element
that contains the column value within a row element. During subsequent
demonstrations, the generalization algorithm uses the generated row
selector to find the row element that contains the column value and
generates a column selector which identifies the corresponding column
element.

At a high level, the generalization algorithm's challenge is to traverse
far enough up in the DOM tree from the demonstrated element to find the
element which corresponds to the row. We solve this using a heuristic;
the basic intuition is to find a large set of elements with similar
parallel structure. Consider the following sample HTML layout, which
displays a truncated table of superheroes, with each row containing some
nested structure:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{\textless{}body\textgreater{}}
    \KeywordTok{\textless{}h1\textgreater{}}\NormalTok{ Team Iron Man }\KeywordTok{\textless{}/h1\textgreater{}}
    \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{’container’}\KeywordTok{\textgreater{}}
        \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}avenger\textquotesingle{}}\KeywordTok{\textgreater{}}
            \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}names\textquotesingle{}}\KeywordTok{\textgreater{}}
                \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Iron Man }\KeywordTok{\textless{}/span\textgreater{}}
                \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}real\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Tony Stark }\KeywordTok{\textless{}/span\textgreater{}}
            \KeywordTok{\textless{}/div\textgreater{}}
           \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{’gender’}\KeywordTok{\textgreater{}}\NormalTok{ Male }\KeywordTok{\textless{}/span\textgreater{}}
        \KeywordTok{\textless{}/div\textgreater{}}
        \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}avenger\textquotesingle{}}\KeywordTok{\textgreater{}}
            \KeywordTok{\textless{}div}\OtherTok{ class=}\StringTok{\textquotesingle{}names\textquotesingle{}}\KeywordTok{\textgreater{}}
                \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}super\_hero\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{  Black Widow }\KeywordTok{\textless{}/span\textgreater{}}
                \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{\textquotesingle{}real\_name\textquotesingle{}}\KeywordTok{\textgreater{}}\NormalTok{ Natalia Romanoff }\KeywordTok{\textless{}/span\textgreater{}}
            \KeywordTok{\textless{}/div\textgreater{}}
            \KeywordTok{\textless{}span}\OtherTok{ class=}\StringTok{’gender’}\KeywordTok{\textgreater{}}\NormalTok{ Female }\KeywordTok{\textless{}/span\textgreater{}}
        \KeywordTok{\textless{}/div\textgreater{}}
\NormalTok{        ...}
    \KeywordTok{\textless{}/div\textgreater{}}
\KeywordTok{\textless{}/body\textgreater{}}
\end{Highlighting}
\end{Shaded}

The user performs a demonstration by clicking on the SPAN element
containing ``Tony Stark.'' Our algorithm traverses upwards from the
demonstrated element, considering each successive parent element as a
potential candidate for the row element. For each parent element \(n\),
the process is as follows:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  compute a selector \(s\) that when executed on \(n\) only returns the
  demonstrated element
\item
  for each sibling \(m\) of \(n\), execute \(s\) on \(m\) and record
  whether the selector returned an element. Intuitively, if the selector
  returns an element, this suggests that the sibling \(m\) has some
  parallel structure to \(n\)
\item
  compute \(n_{siblings}\), the number of sibling elements of \(n\) for
  which \(s\) returned an element
\end{enumerate}
